%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {WebStudio Techleader} % Job title
    {4D SAS} % Organization
    {Rabat, Morocco} % Location
    {Jan. 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Define the architecture of the web application.}
        \item {Built fully automated CI/CD pipelines on Gitlab CI/CD to run the E2E/unit tests, analyse the code quality, build the docker images, and deploy the WebStudio and the technical documentation to the several environments.}
        \item {Implementation of a DAP client to debug a proprietary programming language.}
        \item {Implementation of a LSP client to provide language features like auto complete, go to definition, find all references of a proprietary language.}
        \item {Review the code quality and the technical documentation.}
        \item {Monitor the progress of the team through daily meetings and weekly sprints.}
        \item {Used technologies: Typescript, React, Redux Toolkit, 4D, React Testing Library, Jest, Cypress, Gatsby, Gitlab CI/CD, Docker, Craco, Tailwind, CraftJS, Git, Perforce, TeamCity, Husky}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Service Architect} % Job title
    {4D SAS} % Organization
    {Rabat, Morocco} % Location
    {Dec. 2019 - Nov. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Help the company clients to define the best architecture that meets their needs.}
        \item {write the technical documents defining the technologies to be used.}
        \item {Monitor the technical implementation to make sure to follow the defined architecture.}
        \item {Help 4D Clients to scale their existing applications.}
        \item {Used technologies: Typescript, React, React Native, NodeJS, MongoDB, ExpressJS, Angular, Gitlab CI/CD, Git, Husky, IZMjs, Redis, Nginx}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Technical Consultant} % Job title
    {4D SAS} % Organization
    {Rabat, Morocco} % Location
    {Oct. 2016 - Dec. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Offer advice and technical expertise to the the company in order to help them improve their business performance in terms of maintenance and developer experience.}
        \item {Helping the company's customers to overcome their issues by going on site, analyzing their problems and suggest the most efficient and effective way to solve them.}
        \item {Used technologies: NodeJS, 4D, ExpressJS, Angular, RabbitMQ, Redis, Nginx}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {CTO/Co-Founder}
    {FlexiApps}
    {Rabat, Morocco}
    {Oct. 2014 - Oct. 2016}
    {
      \begin{cvitems}
        \item {Define the high level and the technical architecture of the applications}
        \item {Develop Web applications unsing the MEAN stack}
        \item {Develop mobile applications using the Ionic framework}
        \item {Schedule the projects and the team meetings}
        \item {Write playbooks on Ansible to automate the deployment and the monitoring of clients applications.}
        \item {Develop a dashboard to visualize and monitor clients applications.}
        \item {Used technologies: NodeJS, AngularJS, Mocha/Chai, MongoDB, Gitlab CI/CD, Wakanda, Ionic, Nginx, Redis, RabbitMQ, Ansible}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {4D SAS} % Organization
    {Rabat, Morocco} % Location
    {May 2013 - Apr. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Develop a PaaS solution to help 4D clients to easily deploy their Wakanda applications.}
        \item {Develop a the technical dashboard to monitor the wakanda applications.}
        \item {Used technologies: Wakanda, Node, RabbitMQ, Docker, Nginx, Redis, Git, Bootstrap, BackboneJS, jQuery}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {4D SAS} % Organization
    {Rabat, Morocco} % Location
    {Mar. 2011 - May. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Develop demo applications for Wakanda.}
        \item {Develop server side modules for wakanda server.}
        \item {Develop client side widgets for wakanda studio/server.}
        \item {Used technologies: Wakanda, Git, Perforce, Bootstrap, jQuery}
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
